% Miles A. Curry -- Resume
% Copyright (C) 2014, Miles A. Curry 

% Template originally developed by Emily Dunham
% https://github.com/edunham/resume/blob/master/resume.tex
% You may use and redistribute this as a template, but please leave this
% comment. Change the first two lines to reflect your own information :)

\documentclass[11pt]{article}
\topmargin=0.0in
\textwidth=6.5in
\oddsidemargin=0.0in
\evensidemargin=0in
\headheight=0pt
\headsep=0pt
\textheight=9.5in
\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\begin{document}
\centerline{{\LARGE \bf Miles A. Curry}}

\bigskip

\centerline{email: currymi@onid.orst.edu
        $\bullet$
        irc: currymi on irc.freenode.net}
\centerline{github: MiCurry
        $\bullet$
        \emph{or email me for other contact info}}

\bigskip
\hrulefill
\bigskip

{\Large \bf Employment:}
\begin{description}

\item[Coburg Pizza Company]
    \hfill 06/2013 - 09/2014

    Prepped food for customers to eat in a line style environment.

    Interacted with customers to take orders and solve incorrect orders.

    Prepped ingredients for use during the day.

    Worked with managers and coworkers to schedule and trade shifts.

\item[Computer Helpdesk - OSU College of Forestry]
    \hfill 01/2011 - 05/2013

    Solved user's OSX and Windows (XP, 7) problems in person and over the phone

    Set up/deployed new machines for users using a pixie boot

    Used a ticket notification system to track repairs and user problems
    with other staff members


\item[Eugene Emeralds - Concessions]
    \hfill 06/2011 - 09/2011

    Served and took payment for concession from customers.

\item[Rolf Prima Wheel Systems]
    \hfill 06/2009 - 09/2009

    Built high end specifications

\item[EMPLOYMENT NAME]
    \hfill MM/YEAR - MM/YEAR
       
     EMPLOYMENT DETAILS

\end{description}

\smallskip
\hrulefill
\bigskip

{\Large \bf Education:}
\begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}

    % Update for personal education 
    \item Bachelor of Science, Computer Science, Oregon State University
    \item Cumulative GPA 3.XX, anticipated graduation June 2016

\end{itemize}

\smallskip
\hrulefill
\bigskip

{\Large \bf Extracurriculars:}
\begin{description}
    \item[KBVR-FM DJ]
        \hfill  09/2014 - Present

        Hosted weekly live one-hour radio shows with a theme playlist.

        Hosted weekly one-hour on-air radio shows

        Created themed playlist for shows.

        Worked with station staff and fellow DJ's to schedule shows and
        review music.

        Followed station and FCC rules. %Expand

    \item[Volunteer - Marion and Polk Foodshare]
        \hfill  MM/YEAR - MM/YEAR
        Helped edit food prep instruction in Microsoft Excel.

        Helped prep food for a protein alternative burger.

    \item[Volunteer - Springfield Education Foundation] 
        \hfill MM/YEAR - MM/YEAR

        Set up tables/chairs and sets for charity events.

        Coordinated with event director and other volunteers to set up
        events efficiently and correctly. %kinda vague

    \item[Volunteer - Lane Country Food Bank]
        \hfill MM/YEAR - MM/YEAR

        Packed lunches for a summer food program.

     \item[Volunteer - Worship Musician - The Bridge Open Bible]
        \hfill MM/YEAR - MM/YEAR

        Played Bass Guitar for weekly church worship sessions.

        Communicated with fellow musicians and pastor to lead church in
        worship.

        Communicated with fellow musicians to play music correctly with good
        sound.

        Communicated with worship leader and other bass players to schedule
        days to play and practice.

    \item[NAME OF ACTIVITY]
        \hfill mm/year - mm/year
 
        DESCRIPTION OF ACTIVITIES

\end{description}

{\Large \bf Skills:}
\begin{description}

    \item[Programming]
        C, C++, Bash.

    \item[Linux]
        Familiar with the command line and vim text editors.
        
    \item[Computers]
        Familiar with Mac, Windows and Linux Computers.
        
        Computer competent.

        Efficient with Microsoft Word and competent with excel.
    
\end{description}
{\Large \bf Personal:}
\begin{description}
    \item[Hobbies]
        Running, Biking, Reading, Juggling, Guitar, Electric Bass, Hiking,
        Rock Climbing.

\end{description}
\end{document}
