% Miles A. Curry -- Resume
% Copyright (C) 2014, Miles A. Curry 

% Template originally developed by Emily Dunham
% https://github.com/edunham/resume/blob/master/resume.tex
% You may use and redistribute this as a template, but please leave this
% comment. Change the first two lines to reflect your own information :)

\documentclass[11pt]{article}
\topmargin=0.0in
\textwidth=6.5in
\oddsidemargin=0.0in
\evensidemargin=0in
\headheight=0pt
\headsep=0pt
\textheight=9.5in
\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\begin{document}
\centerline{{\LARGE \bf Miles A. Curry}}

\bigskip

\centerline{email: currymi@onid.orst.edu
        $\bullet$
        irc: currymi on irc.freenode.net}
\centerline{gitHub: MiCurry
        $\bullet$
        cell: 541-206-7583}

\bigskip
\hrulefill
\bigskip


\smallskip
\hrulefill
\bigskip

{\Large \bf Education:}
\begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}

    % Update for personal education 
    \item Bachelor of Science, Computer Science, Oregon State University
    \item Cumulative GPA 3.40 Core GPA, anticipated graduation June 2016

\end{itemize}

\smallskip
\hrulefill
\bigskip

{\Large \bf Employment:}
\begin{description}

\item[Computer Helpdesk - OSU College of Forestry]
    \hfill 01/2011 - 05/2013

    Solved user's OSX and Windows (XP, 7) problems in person and over the phone.

    Wrote an OSX AppleScript to connect to the College's Virtual Private
    Network.

    Used a ticket notification system to track user repairs and problems
    with other members of the IT department.

\item[Eugene Emeralds - Concessions]
    \hfill 07/2011 - 09/2011

    Served customers concessions during daily baseball games.

\end{description}
{\Large \bf Skills:}
\begin{description}

    \item[Programming] 
    \hfill

        Very accustomed to constructing programs in C and using C system calls.

        Familiar creating scripts in the Python scripting language.

        Experience creating and querying MySQL databases.

        Written several mathematic programs in MASM Assembly Language

    \item[Linux]
    \hfill
    
        Programs efferently and most often in a Linux command line environment.

        Highly proficient and knowledge of the Vim text editor and GNU utilities

    \item[Computers] 
    \hfill

        Familiar with using  Mac, Windows and Linux PCs.
        
        Efficient with Microsoft Word and LaTeX word processors.

\end{description}
{\Large \bf Extracurriculars \& Personal:}
\begin{description}

    \item[KBVR-FM DJ]
        \hfill  09/2014 - Present

        Hosts a weekly live one-hour radio shows with a themed music playlist.

        Worked with station staff and fellow DJ's to schedule shows and
        review new station music.

    \item[Hobbies]
    \hfill

        Running, Biking, Reading, Juggling, Music, Guitar, Electric Bass, Hiking,
        Rock Climbing, Meditation.
    
\end{description}

\end{document}
